\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal Shakeup

### 2025-03-22 code/paper.qmd
final paper

We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data.
There appears to be a noticeable peak in activity during the middle of the week.
However, we don't have enough data across weeks to conclusively say it is due to the day of the week itself.
It is more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
The two peaks in our graph could be attributed to two major news stories.
On March 5th, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6th, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

@@

The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections while excluding our keyword search terms.
These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
Examining this visual reveals that in posts the current president's name is the top word.
However, in both posts and comments, there appears to be an emerging theme of community as words like people, employees, service, care, jobs, and public are also top words.
This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.

>>>>

We show the number of posts pre/post processing by day in Figure 1 during the timeframe that we collected these data.
There appears to be a noticeable peak in activity during the middle of the week.
However, we do not have enough data across weeks to conclusively say it is due to the day of the week itself.
It is more likely that these spikes are linked to specific events that occurred on those days, which sparked conversations.
The two peaks in our graph could be attributed to two major news stories.
On March 5th, Elon Musk made a statement about wanting to "save Western civilization from empathy," and on March 6th, there were reports that President Trump was limiting Musk's authority due to backlash over cuts to DOGE.
These events likely had a significant impact on the volume of Reddit posts related to Elon Musk and DOGE, driving the observed spikes in activity.

@@

The graphs below (Figure 4) show the most frequent words used in both Reddit posts and their comment sections while excluding our keyword search terms.
These words were identified by tokenizing the text and removing stop words, then counting the occurrences of the most common terms.
The removal of stop words allowed us to focus on contextual words in the posts/comments rather than common words like "the" and "and" that are not useful in these types of analysis.
Examining this visual reveals that in posts the current president's name is the top word.
However, in both posts and comments, there appears to be an emerging theme of community as words like people, employees, service, care, jobs, and public are also top words.
This highlights the focus of the community on these key themes, reflecting the ongoing conversations and interests of Reddit users within this context.

### 2025-03-22 code/paper.tex
final paper

\date{March 21, 2025}
\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
Shakeup}
\author{
Kevin Linares\\
University of Maryland\\
and\\Felix Baez-Santiago\\
and\\Aria Lu\\
and\\Gloria Zhou\\
University of Michigan\\
}
\maketitle

@@

We show the number of posts pre/post processing by day in Figure 1
during the timeframe that we collected these data. There appears to be a
noticeable peak in activity during the middle of the week. However, we
don't have enough data across weeks to conclusively say it is due to the
day of the week itself. It is more likely that these spikes are linked
to specific events that occurred on those days, which sparked
conversations. The two peaks in our graph could be attributed to two
major news stories. On March 5th, Elon Musk made a statement about
wanting to ``save Western civilization from empathy,'' and on March 6th,
there were reports that President Trump was limiting Musk's authority
due to backlash over cuts to DOGE. These events likely had a significant
impact on the volume of Reddit posts related to Elon Musk and DOGE,
driving the observed spikes in activity.

@@

The graphs below (Figure 4) show the most frequent words used in both
Reddit posts and their comment sections while excluding our keyword
search terms. These words were identified by tokenizing the text and
removing stop words, then counting the occurrences of the most common
terms. Examining this visual reveals that in posts the current
president's name is the top word. However, in both posts and comments,
there appears to be an emerging theme of community as words like people,
employees, service, care, jobs, and public are also top words. This
highlights the focus of the community on these key themes, reflecting
the ongoing conversations and interests of Reddit users within this
context.

>>>>

\date{March 22, 2025}
\title{\bf DOGE Days on Reddit: Decoding Public Sentiment in a Federal
Shakeup}
\author{
Kevin Linares\\
University of Maryland\\
and\\Felix Baez-Santiago\\
and\\Aria Lu\\
and\\Gloria Zhou\\
University of Michigan\\
}
\maketitle

@@

We show the number of posts pre/post processing by day in Figure 1
during the timeframe that we collected these data. There appears to be a
noticeable peak in activity during the middle of the week. However, we
do not have enough data across weeks to conclusively say it is due to
the day of the week itself. It is more likely that these spikes are
linked to specific events that occurred on those days, which sparked
conversations. The two peaks in our graph could be attributed to two
major news stories. On March 5th, Elon Musk made a statement about
wanting to ``save Western civilization from empathy,'' and on March 6th,
there were reports that President Trump was limiting Musk's authority
due to backlash over cuts to DOGE. These events likely had a significant
impact on the volume of Reddit posts related to Elon Musk and DOGE,
driving the observed spikes in activity.

@@

The graphs below (Figure 4) show the most frequent words used in both
Reddit posts and their comment sections while excluding our keyword
search terms. These words were identified by tokenizing the text and
removing stop words, then counting the occurrences of the most common
terms. The removal of stop words allowed us to focus on contextual words
in the posts/comments rather than common words like ``the'' and ``and''
that are not useful in these types of analysis. Examining this visual
reveals that in posts the current president's name is the top word.
However, in both posts and comments, there appears to be an emerging
theme of community as words like people, employees, service, care, jobs,
and public are also top words. This highlights the focus of the
community on these key themes, reflecting the ongoing conversations and
interests of Reddit users within this context.
